draft_yma

### 2021-12-14 draft_yma.Rmd
forwar, backward with trans

# Global
skimr::skim(cdi_descriptive) %>% 
  select(-c("skim_type","complete_rate")) %>% 
    mutate(skim_variable = 
             recode(skim_variable, pcincome = "pcincome (in dollars)", totalinc = "totalinc (in million of dollars)"
  )) %>% 
  knitr::kable(
    col.names = c("variable", "n_missing", "mean","sd","min","Q25","median","Q75","max","histogram"),
    caption = "Global Summary", digits = 4)

ggplot(gather(cdi_descriptive), aes(value)) + 
    geom_histogram(bins = 13) + 
    facet_wrap(~key, scales = 'free_x')
```

@@

```{r}
par(mfrow = c(3,5))

@@

```{r}
cdi %>% 
  ggplot(aes(x = crm_1000)) +
  geom_histogram()

# log transfor the outcome
cdi %>% 
  ggplot(aes(x = log(crm_1000))) +
  geom_histogram()

@@

```{r}
fit_back = step(trans_fit, direction='backward')
fit_back
```

@@

```{r}
fit_forward = step(trans_fit, direction='forward')
fit_forward
```

@@

```{r}
fit_both = step(trans_fit, direction='both')
fit_both
```

crm_1000 ~ pop + pop18 + hsgrad + bagrad + poverty + 
    pcincome + region + pbeds_1000 + density_pop, data = cdi_model
This gives back the same model as back

Some group forward again based on their first time step wise...not sure if we need to do that tho

@@

>>>>

# Global
skimr::skim(cdi_descriptive) %>% 
  select(-c("skim_type","complete_rate")) %>% 
    mutate(skim_variable = 
             recode(skim_variable, pcincome = "pcincome (in dollars)", totalinc = "totalinc (in million of dollars)"
  )) %>% 
  knitr::kable(
    col.names = c("variable", "n_missing", "mean","sd","min","Q25","median","Q75","max","histogram"),
    caption = "Global Summary", digits = 4)
```

@@

```{r}
par(mfrow = c(2,7))

@@

```{r}
cdi %>% 
  ggplot(aes(x = crm_1000)) +
  geom_histogram()
```

@@

```{r}
fit_back = step(trans_fit, direction='backward')
fit_back

olsrr::ols_plot_resid_fit(fit_back)
olsrr::ols_plot_resid_qq(fit_back)
MASS::boxcox(fit_back)
```

lm(formula = crm_1000^0.5 ~ pop + pop18 + hsgrad + bagrad + poverty + 
    pcincome + region + pbeds_1000 + density_pop, data = cdi_model)

@@

```{r}
fit_forward = step(trans_fit, direction='forward')
fit_forward

olsrr::ols_plot_resid_fit(fit_forward)
olsrr::ols_plot_resid_qq(fit_forward)
MASS::boxcox(fit_forward)
```

lm(formula = crm_1000^0.5 ~ pop + pop18 + pop65 + hsgrad + bagrad + 
    poverty + unemp + pcincome + region + pdocs_1000 + pbeds_1000 + 
    density_pop, data = cdi_model)

@@

```{r}
fit_both = step(trans_fit, direction='both')
fit_both
```
lm(formula = crm_1000^0.5 ~ pop + pop18 + hsgrad + bagrad + poverty + 
    pcincome + region + pbeds_1000 + density_pop, data = cdi_model)

This gives back the same model as back

@@

## backward by hand

```{r}
# No docs
step1 = update(full_fit, . ~ . -pdocs_1000)
summary(step1)

# No pop65
step2 = update(step1, . ~ . -pop65)
summary(step2)

# No unemp
step3 = update(step2, . ~ . -unemp)
summary(step3)

mult.fit.final = lm(formula = crm_1000 ~ pop + pop18 + hsgrad + bagrad + poverty + 
    pcincome + region + pbeds_1000 + density_pop, data = cdi_model)
summary(mult.fit.final)
```
